### 2023-04-04 src/docs_paper/appendix.Rmd
Add simplified Naomi DAG template, fix error with algorithm flowchart, add to appendix

@@

>>>>

# Inferential algorithm

```{r algorithm-flowchart, fig.cap="Flowchart describing the algorithm we propose (work in progress)."}
knitr::include_graphics("depends/algorithm-flowchart.pdf")
```

@@

```{r simplified-naomi, fig.cap="Directed acyclic graph describing the simplified Naomi model (work in progress)."}
knitr::include_graphics("depends/simplified-naomi.pdf")
```

### 2023-04-04 src/docs_paper/paper.Rmd
Add simplified Naomi DAG template, fix error with algorithm flowchart, add to appendix

<!-- * [ ] Tying together Naomi model within LGM / ELGM mathematical notation -->
<!-- * [ ] Create DAG representing Naomi model -->
<!-- * [ ] Rewrite section on why Naomi is an ELGM, drawing from slides -->
<!-- * [ ] Write section on Laplace approximation -->
<!-- * [ ] Write section on AGHQ, tying together connection to Laplace for k = 1 -->
<!-- * [ ] Move algorithm to algorithm environment -->

>>>>

<!-- * [ ] Tying together Naomi model within LGM / ELGM mathematical notation -->
<!-- * [ ] Create DAG representing Naomi model. This would likely go into the appenxix, so use that notation -->
<!-- * [ ] Rewrite section on why Naomi is an ELGM, drawing from slides -->
<!-- * [ ] Write section on Laplace approximation -->
<!-- * [ ] Write section on AGHQ, tying together connection to Laplace for k = 1 -->
<!-- * [ ] Move algorithm to algorithm environment -->

### 2023-04-04 src/plot-tikz_algorithm-flowchart/algorithm-flowchart.tex
Add simplified Naomi DAG template, fix error with algorithm flowchart, add to appendix

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning}
\usepackage{bm}

@@

\tikzstyle{question} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
\tikzstyle{category} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
\tikzstyle{container} = [rectangle, draw, rounded corners, dashed, inner sep=2em]
\tikzstyle{line} = [draw, -latex']

\begin{tikzpicture}[node distance = 2cm, auto]

    \node[category] at (0, 0) (1) {$p(\theta, \x, \y)$};

    % x
    \node[category] at (0, -3) (a) {$\tilde p_{\text{LA}}(x_i, \btheta, \y)$};
    \node[category] at (0, -6) (b) {$\tilde p_{\text{AQ}}(x_i, \y)$};
    \node[category] at (0, -9) (c) {$\tilde p_{\text{AQ}}(x_i \, | \, \y)$};
    \node[category] at (0, -12) (d) {Image of a nice curve};
    \path[line] (1) -- node[align=center] {Laplace approximation\\Integrate out $\tilde p_{\text{G}}(\x_{-i} \, | \, x_i, \btheta, \y)$}(a);
    \path[line] (a) -- node[align=center] {Integrate out $\theta$\\$\sum_\z \tilde p_{\text{LA}}(x_i, \btheta(\z), \y) \omega(\z)$}(b);
    \path[line] (b) -- node[align=center] {Normalise}(c);
    \path[line] (c) -- node[align=center] {Evaluate $k = 7$ AGHQ nodes\\Use spline interpolation}(d);

    % theta
    \node[category] at (8, 0) (2) {$\tilde p_{\text{LA}}(\btheta, \y)$};
    \node[category] at (8, -3) (3) {$\tilde p_{\text{AQ}}(\y)$};
    \node[category] at (8, -6) (4) {$\tilde p_{\text{AQ}}(\btheta \, | \, \y)$};
    \node[category] at (8, -9) (5) {$\tilde p_{\text{AQ}}(\theta_j \, | \, \y)$};
    \node[category] at (8, -12) (6) {Image of a nice curve};
    \path[line] (1) -- node[align=center] {Laplace approximation\\Integrate out $\tilde p_{\text{G}}(\x \, | \, \btheta, \y)$}(2);
    \path[line] (2) -- node[align=center] {Integrate out $\btheta$ with AGHQ\\Nodes $\z \in \mathcal{Q}(m, k)$\\Adapted $\btheta(\z) = \hat{\btheta} + Lz$\\Weights $\omega(\z):\mathcal{Q} \to \mathbb{R}$}(3);
    \path[line] (3) -- node[align=center] {Normalise} (4);
    \path[line] (2) edge[bend left] node [left] {} (4);
    \path[line] (3) -- (c);
    \path[line] (4) -- node[align=center] {Marginalise} (5);
    \path[line] (5) -- node[align=center] {Evaluate $k = 7$ AGHQ nodes\\Use spline interpolation}(6);

\end{tikzpicture}

>>>>

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning}

@@

\tikzstyle{category} = [rectangle, draw, text width=10em, text centered, rounded corners, minimum height=4em]
\tikzstyle{container} = [rectangle, draw, rounded corners, dashed, inner sep=2em]
\tikzstyle{line} = [draw, -latex']

\begin{tikzpicture}[node distance = 2cm, auto]
  \node[category] at (0, 0) (1) {$p(\btheta, \x, \y)$};
  \node[category] at (0, -3) (a) {$\tilde p_{\texttt{LA}}(x_i, \btheta, \y)$};
  \node[category] at (0, -6) (b) {$\tilde p_{\texttt{AQ}}(x_i, \y)$};
  \node[category] at (0, -9) (c) {$\tilde p_{\texttt{AQ}}(x_i \, | \, \y)$};
  \node[category] at (0, -12) (d) {Image of a nice curve};
  \path[line] (1) -- node[align=center] {Laplace approximation\\Integrate out $\tilde p_{\texttt{G}}(\x_{-i} \, | \, x_i, \btheta, \y)$}(a);
  \path[line] (a) -- node[align=center] {Integrate out $\theta$\\$\sum_\z \tilde p_{\texttt{LA}}(x_i, \btheta(\z), \y) \omega(\z)$}(b);
  \path[line] (b) -- node[align=center] {Normalise}(c);
  \path[line] (c) -- node[align=center] {Evaluate $k = 7$ AGHQ nodes\\Use spline interpolation}(d);
  \node[category] at (8, 0) (2) {$\tilde p_{\texttt{LA}}(\btheta, \y)$};
  \node[category] at (8, -3) (3) {$\tilde p_{\texttt{AQ}}(\y)$};
  \node[category] at (8, -6) (4) {$\tilde p_{\texttt{AQ}}(\btheta \, | \, \y)$};
  \node[category] at (8, -9) (5) {$\tilde p_{\texttt{AQ}}(\theta_j \, | \, \y)$};
  \node[category] at (8, -12) (6) {Image of a nice curve};
  \path[line] (1) -- node[align=center] {Laplace approximation\\Integrate out $\tilde p_{\texttt{G}}(\x \, | \, \btheta, \y)$}(2);
  \path[line] (2) -- node[align=center] {Integrate out $\btheta$ with AGHQ\\Nodes $\z \in \mathcal{Q}(m, k)$\\Adapted $\btheta(\z) = \hat{\btheta} + Lz$\\Weights $\omega(\z): \mathcal{Q} \to \mathbb{R}$}(3);
  \path[line] (3) -- node[align=center] {Normalise} (4);
  \path[line] (2) edge[bend left] node [left] {} (4);
  \path[line] (3) -- (c);
  \path[line] (4) -- node[align=center] {Marginalise} (5);
  \path[line] (5) -- node[align=center] {Evaluate $k = 7$ AGHQ nodes\\Use spline interpolation}(6);
\end{tikzpicture}
